A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-09 main.tex
Sync.
Revice until run.

% transition variable

The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable}.
It is used to show the thickness of brackets.
For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$ becomes $(\lambda x:\I.x+10)$ after it was run it twice.
\red{run twiceは表現が微妙}

% transition

A sequence of transition variables is a transition which is called a stage in \LMD.
In \LTP, all judgment has a transition.
Especially, terms without quoting exist at the empty transition which is represented by $\epsilon$.
For example, $(\lambda x:\I.x)\ (1+2)$ is at $\epsilon$ transition and 
$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.

@@

There are abstractions for transition variables and applications for transition abstraction in \LTP.
They look like $\Lambda\alpha.M$ and $M\ A$, respectively.
A transition abstraction binds a transition variable in a term.
For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
It is only natural there is a rule for transition application in \LTP.
The rule is the following.

\begin{align*}
    (\Lambda\alpha.M)\ A \longrightarrow M[\alpha\mapsto A]
\end{align*}

For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.
Although we can apply any transition to a transition abstraction in \LTP,
we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.
\red{この文はここに来るべきなのか? LTPの説明ではないが}

% transition-related symbols disappear when the empty transition is substituted.

Another important rule about a transition variable is 
that a transition variable related symbol disappears when the empty transition is substituted to the transition variable.
For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
This rule is applied all transition variable related symbols: $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$.

% Run
The main purpose of transition abstractions and transition applications are to represent {\bf{run}} operator.
In multistage calculus, {\bf{run}} is a very important operator.
It changes quoted code to the original code.
{\bf{run}} is realized with application of the empty transition $\epsilon$.
For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
because $\TB_\epsilon$ is disappeared.

@@

\red{, which is called a \textit{stage variable} in \LMD.}

>>>>

% transition variable and transition

The subscript $\alpha$ in $\TB_\alpha M$ is a \textit{transition variable} and
a sequence of transition variables is called \textit{transition}.
They are used to show the thickness of brackets.
For example, $\TB_\alpha (\lambda x:\I.x+10)$ is the fragment of code which becomes $(\lambda x:\I.x+10)$ after it was run once and
$\TB_\alpha \TB_\beta (\lambda x:\I.x+10)$, which is abbreviated as $\TB_{\alpha\beta} (\lambda x:\I.x+10)$,
 becomes $(\lambda x:\I.x+10)$ after it was run it twice.
\red{run twiceは表現が微妙}

There are abstractions for transition variables and applications for transition abstraction in \LTP.
They look like $\Lambda\alpha.M$ and $M A$, respectively.
A transition abstraction binds a transition variable in a term.
For example, all $\alpha$ in $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))$ are bound.
It is only natural there is a reduction rule for transition application in \LTP.
The rule is the following.
\begin{align*}
    (\Lambda\alpha.M)\ A \longrightarrow M[\alpha\mapsto A]
\end{align*}
For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ (\beta\gamma)$ reduces to $\TB_{\beta\gamma} (\lambda x:\I.x)$.

% transition-related symbols disappear when the empty transition is substituted.
% In short, about "run"

Another important rule about a transition variable is 
that symbols with transition variables disappear 
when the empty transition $\epsilon$ is substituted to the transition variable.
The purpose of this rule is express \verb|run| without any special symbol.
In multistage calculus, \verb|run| is a very important operator which changes quoted code to the original code.
For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
In \LTP, \verb|run| is realized with application of the empty transition $\epsilon$.

In \LTP, all judgment has a transition.
Especially, terms without quoting exist at the empty transition which is represented by $\epsilon$.
For example, $(\lambda x:\I.x)\ (1+2)$ is at $\epsilon$ transition and 
$\TB_\alpha (\lambda x:\I.x)$ is at $\alpha$ transition.

@@

@@

\red{, which is called a \textit{stage variable} in \LMD.}
\red{ which is called a stage in \LMD.}
\red{Although we can apply any transition to a transition abstraction in \LTP,
we restrict the transitions only to $\epsilon$ transition in \LMD to simplify the system.}
